### 2020-04-09 system-model.tex
:pencil: Energy harvester

		\begin{subsubsection} {Modulated Information Waveform}
			Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+(n-1) \Delta f$ ($n = 1,\dots,N$). The information symbol $\tilde{x}_{I,n}$ on subband $n$ is a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance (i.e. $\tilde{x}_{I,n} \sim \mathcal{CN}(0,1)$). Denote $w_{I,n} = s_{I,n} e^{j\phi_{I,n}}$ as the information weight on the $n$-th subcarrier with magnitude $s_{I,n}$ and phase $\phi_{I,n}$, the corresponding modulated symbol can be expressed as $x_{I,n} = \tilde{s}_{I,n} e^{j\tilde{\phi}_{I,n}}$, with $\tilde{s}_{I,n} = s_{I,n} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n} = \phi_{I,n} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e. $x_{I,n} \sim \mathcal{CN}(0,s_{I,n}^2)$). Therefore, the transmit information waveform at time $t$ writes as
			\begin{equation}	\label{eq:x_{I}(t)}
				\begin{split}
					x_{I}(t)
					&= \sum_{n=1}^{N} \tilde{s}_{I,n}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n}(t) \right)	\\
					&= \Re \left\{ \sum_{n=1}^{N} x_{I,n}(t) e^{j2 \pi f_n t} \right\}	\\
					&= \Re \left\{ \sum_{n=1}^{N} w_{I,n} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
				\end{split}
			\end{equation}
			% On top of this, the information waveform vector is spread over $M$ antennas
			% \begin{equation}	\label{eq:x_I(t)}
			% 	\boldsymbol{x}_I(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{I,n}\tilde{x}_n(t) e^{j2{\pi}{f_n}t} \right\}
			% \end{equation}
			% where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T \in \mathbb{C}^{M \times 1}$.
		\end{subsubsection}

		\begin{subsubsection} {Unmodulated Power Waveform}
			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant (i.e. $\tilde{x}_{P,n} = 1$). Therefore, the power weight $w_{P,n} = s_{P,n} e^{j\phi_{P,n}}$ represents the complex-valued sinewave (i.e. $x_{P,n}(t) = w_{P,n}$) in the baseband (BB). The transmit power waveform at time $t$ is given by
			\begin{equation}	\label{eq:x{P}(t)}
				\begin{split}
					x_{P}(t)
					&= \sum_{n=1}^{N} s_{P,n}(t) \cos \left( 2 \pi f_n t + \phi_{P,n}(t) \right)	\\
					&= \Re \left\{ \sum_{n=1}^{N} x_{P,n}(t) e^{j2 \pi f_n t} \right\}	\\
					&= \Re \left\{ \sum_{n=1}^{N} w_{P,n} e^{j2 \pi f_n t} \right\}
				\end{split}
			\end{equation}
			% Similarly, the corresponding power waveform vector is stacked across $M$ transmit antennas as
			% \begin{equation}	\label{eq:x_P(t)}
			% 	\boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
			% \end{equation}
			% where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
		\end{subsubsection}

@@

		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. Specifically, the frequency response of direct and reflective links at subband $n$ are $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,n,l}=[h_{R,1,n,l},\dots,h_{R,K,n,l}]^T \in \mathbb{C}^{K \times 1}$. Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. We also denote the direct and reflective links of user $k$ as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}] \in \mathbb{C}^{1 \times N}$ and $\boldsymbol{h}_{R,k}=[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}] \in \mathbb{C}^{1 \times NL}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Therefore, it holds that $\boldsymbol{H}_D=[\boldsymbol{h}_{D,1},\dots,\boldsymbol{h}_{D,N}]=[\boldsymbol{h}_{D,1}^T,\dots,\boldsymbol{h}_{D,K}^T]^T$, $\boldsymbol{H}_I=[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}]$, and $\boldsymbol{H}_R=[\boldsymbol{H}_{R,1},\dots,\boldsymbol{H}_{R,N}]=[\boldsymbol{h}_{R,1}^T,\dots,\boldsymbol{h}_{R,K}^T]^T$.
		Element $l$ of the IRS receives a superposed waveform through the multipath channel and redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. We construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands as $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and AP-IRS-user link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}	\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}	\label{eq:h_{k,n}}
			h_{k,n}=h_{D,n,k}+\boldsymbol{h}_{R,k}\boldsymbol{\Theta}\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
		\begin{equation}	\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R}\boldsymbol{\Theta}\boldsymbol{h}_{I,n}
		\end{equation}
		It is interesting to notice that the total frequency response at subband $n$ depends on the reflective channel across all $N$ subbands such that the frequency selectivity only comes from the direct and incident links. From another perspective, the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times N}$ for user $k$ writes as
		\begin{equation}	\label{eq:h_k}
			\boldsymbol{h}_k=\boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k}\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		Therefore, we have $\boldsymbol{H}=[\boldsymbol{h}_1,\dots,\boldsymbol{h}_N]=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_K^T]^T$.
	\end{subsection}

	\begin{subsection}	{Received Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}	\label{eq:y_{k}(t)}
			\begin{split}
				y_{k}(t)
				&=y_{I,k}(t)+y_{P,k}(t)	\\
				&=\Re\left\{{\sum_{n=1}^N{(w_{I,n}\tilde{x}_{I,n}(t)+w_{P,n})h_{k,n}e^{j2{\pi}{f_n}t}}}\right\}
				% &=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
			\end{split}
		\end{equation}
	\end{subsection}

	\begin{subsection}	{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}	\label{eq:I_k}
			\begin{split}
				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
				&=?
			\end{split}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:I_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

	\begin{subsection}	{Energy Harvester}
		Although the power term $y_{P,k}(t)$ have no impact on communication, both $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to energy delivery in different manner. Consider the nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
		\begin{equation}	\label{eq:i_k}
			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
		\end{equation}
		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna. With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components. \cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
		\begin{equation}	\label{eq:z_{DC,k}}
			\begin{split}
				z_{DC,k}
				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}	\\
				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_{P,k}(t)^i\right\}}	\\
				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)^i\right\}\right\}}
			\end{split}
		\end{equation}
		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.

>>>>

		\begin{subsubsection} {Modulated Information Waveform}
			Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+(n-1) \Delta f$ ($n = 1,\dots,N$). The information symbol $\tilde{x}_{I,n}$ on subband $n$ is a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance (i.e. $\tilde{x}_{I,n} \sim \mathcal{CN}(0,1)$). Denote $w_{I,n} = s_{I,n} e^{j\phi_{I,n}}$ as the information weight on the $n$-th subcarrier with magnitude $s_{I,n}$ and phase $\phi_{I,n}$, the corresponding modulated symbol can be expressed as $x_{I,n} = \tilde{s}_{I,n} e^{j\tilde{\phi}_{I,n}}$, with $\tilde{s}_{I,n} = s_{I,n} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n} = \phi_{I,n} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e. $x_{I,n} \sim \mathcal{CN}(0,s_{I,n}^2)$). Collect $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N \times 1}$. Therefore, the transmit information waveform at time $t$ writes as
			\begin{equation}	\label{eq:x_{I}(t)}
				\begin{split}
					x_{I}(t)
					&= \sum_{n=1}^{N} \tilde{s}_{I,n}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n}(t) \right)	\\
					&= \Re \left\{ \sum_{n=1}^{N} x_{I,n}(t) e^{j2 \pi f_n t} \right\}	\\
					&= \Re \left\{ \sum_{n=1}^{N} w_{I,n} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
				\end{split}
			\end{equation}
			% On top of this, the information waveform vector is spread over $M$ antennas
			% \begin{equation}	\label{eq:x_I(t)}
			% 	\boldsymbol{x}_I(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{I,n}\tilde{x}_n(t) e^{j2{\pi}{f_n}t} \right\}
			% \end{equation}
			% where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T \in \mathbb{C}^{M \times 1}$.
		\end{subsubsection}

		\begin{subsubsection} {Unmodulated Power Waveform}
			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant (i.e. $\tilde{x}_{P,n} = 1$). Therefore, the power weight $w_{P,n} = s_{P,n} e^{j\phi_{P,n}}$ represents the complex-valued sinewave (i.e. $x_{P,n}(t) = w_{P,n}$) in the baseband (BB). Collect $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N \times 1}$. The transmit power waveform at time $t$ is given by
			\begin{equation}	\label{eq:x{P}(t)}
				\begin{split}
					x_{P}(t)
					&= \sum_{n=1}^{N} s_{P,n}(t) \cos \left( 2 \pi f_n t + \phi_{P,n}(t) \right)	\\
					&= \Re \left\{ \sum_{n=1}^{N} x_{P,n}(t) e^{j2 \pi f_n t} \right\}	\\
					&= \Re \left\{ \sum_{n=1}^{N} w_{P,n} e^{j2 \pi f_n t} \right\}
				\end{split}
			\end{equation}
			% Similarly, the corresponding power waveform vector is stacked across $M$ transmit antennas as
			% \begin{equation}	\label{eq:x_P(t)}
			% 	\boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
			% \end{equation}
			% where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
		\end{subsubsection}

@@

		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. Specifically, the frequency response of direct and reflective links at subband $n$ are $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,n,l}=[h_{R,1,n,l},\dots,h_{R,K,n,l}]^T \in \mathbb{C}^{K \times 1}$. Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. We also denote the direct and reflective links of user $k$ as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}] \in \mathbb{C}^{1 \times N}$ and $\boldsymbol{h}_{R,k}=[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}] \in \mathbb{C}^{1 \times NL}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Therefore, it holds that $\boldsymbol{H}_D=[\boldsymbol{h}_{D,1},\dots,\boldsymbol{h}_{D,N}]=[\boldsymbol{h}_{D,1}^T,\dots,\boldsymbol{h}_{D,K}^T]^T$, $\boldsymbol{H}_I=[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}]$, and $\boldsymbol{H}_R=[\boldsymbol{H}_{R,1},\dots,\boldsymbol{H}_{R,N}]=[\boldsymbol{h}_{R,1}^T,\dots,\boldsymbol{h}_{R,K}^T]^T$.
		Element $l$ of the IRS receives a superposed waveform through the multipath channel and redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. We construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands as $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and AP-IRS-user link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}	\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}	\label{eq:h_{k,n}}
			h_{k,n}=h_{D,n,k}+\boldsymbol{h}_{R,k}\boldsymbol{\Theta}\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
		\begin{equation}	\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R}\boldsymbol{\Theta}\boldsymbol{h}_{I,n}
		\end{equation}
		It is interesting to notice that the frequency response at subband $n$ depends on the reflective channel across all $N$ subbands such that the frequency selectivity only comes from the direct and incident links. From another perspective, the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times N}$ for user $k$ writes as
		\begin{equation}	\label{eq:h_k}
			\boldsymbol{h}_k=\boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k}\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		Therefore, we have $\boldsymbol{H}=[\boldsymbol{h}_1,\dots,\boldsymbol{h}_N]=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_K^T]^T$.
	\end{subsection}

	\begin{subsection}	{Received Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}	\label{eq:y_k(t)}
			\begin{split}
				y_k(t)
				&=y_{I,k}(t)+y_{P,k}(t)	\\
				&=\Re\left\{{\sum_{n=1}^N{(w_{I,n}\tilde{x}_{I,n}(t)+w_{P,n})h_{k,n}e^{j2{\pi}{f_n}t}}}\right\}
				% &=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
			\end{split}
		\end{equation}

		% \begin{equation}	\label{eq:y_k**2(t)}
		% 	\begin{split}
		% 		\mathcal{A}\left\{y_{P,k}^2(t)=\frac{1}{2}\right\}
		% 		&=\Re\left\{\sum_{n_1,n_2}\right\}
		% 	\end{split}
		% \end{equation}
	\end{subsection}

	\begin{subsection}	{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}	\label{eq:I_k}
			\begin{split}
				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
				% &=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}{\sigma_n^2}\right)}
			\end{split}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:I_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

	\begin{subsection}	{Energy Harvester}
		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to power transfer in different manners. Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
		\begin{equation}	\label{eq:i_k}
			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}_{\tilde{x}_n}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
		\end{equation}
		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna. Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ are determined such that the randomness comes from the input distribution $\tilde{x}_n$. Therefore, we first extract the DC component based on $h_{k,n}$, $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ by $\mathcal{A}\left\{.\right\}$ and then consider the expectation over $\tilde{x}_n$ by $\mathcal{E}\left\{.\right\}$. With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ which has no contribution to DC components. \cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
		\begin{equation}	\label{eq:z_k}
			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
		\end{equation}
		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage. We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy delivery. Since $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^3(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}^3(t)\right\}\right\}=0$ and $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)y_{P,k}^2(t)\right\}\right\}=\mathcal{A}\left\{\mathcal{E}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}$, the target function $z_k$ reduces to \ref{eq:z_k_truncated}	\\
		\begin{strip}
			\begin{equation}	\label{eq:z_k_truncated}
				\begin{split}
					z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)
					&={k_2}{\rho}{R_{\text{ant}}}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}	\\
					&\quad+{k_2}{\rho}{R_{\text{ant}}}\mathcal{A}\left\{y_{P,k}^2(t)\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{A}\left\{y_{P,k}^4(t)\right\}	\\
					&\quad+6{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}
				\end{split}
			\end{equation}
		\end{strip}
		whose terms are expressed in \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4}}	\\
		\begin{strip}
			\begin{align}
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\} & =\frac{1}{2}\sum_n{(w_{I,n}h_{k,n})(w_{I,n}h_{k,n})^*}	\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                  \\
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\} & =\frac{3}{4}\sum_{{n_1},{n_2}}{(w_{I,{n_1}}h_{k,{n_1}})(w_{I,{n_2}}h_{k,{n_2}})(w_{I,{n_1}}h_{k,{n_1}})^*(w_{I,{n_2}}h_{k,{n_2}})^*}	\label{eq:E{A{y_{I,k}**4}}}                                                                    \\
				\mathcal{A}\left\{y_{P,k}^2(t)\right\}                           & =\frac{1}{2}\sum_n{(w_{P,n}h_{k,n})(w_{P,n}h_{k,n})^*}	\label{eq:A{y_{P,k}**2}}                                                                                                                                                     \\
				\mathcal{A}\left\{y_{P,k}^4(t)\right\}                           & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{n_1}}h_{k,{n_1}})(w_{P,{n_2}}h_{k,{n_2}})(w_{P,{n_3}}h_{k,{n_3}})^*(w_{P,{n_4}}h_{k,{n_4}})^*}	\label{eq:A{y_{P,k}**4}}
			\end{align}
		\end{strip}
		Note that $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^4\right\}=2$. The latter provides a modulation gain to the nonlinear terms in the output DC current.
